HO unification from object language to meta language

### 2024-04-04 paper/main.tex
tex : solved a todo

% make test ONLY=7004 TEX=tex
\printAlll
  {{{X,\lambda x.x},
    {\lambda x.(Y\appsep (X\appsep x)),a}}}
  {{{A,\lambda x.x},
    {B,a}}}
  {{{Y,D,0},
    {X,A,0}}}
  {{{\eta,,A,\lambda x.E_{x}},
    {\eta,,B,\lambda x.C_{x}},
    {\beta,x,C_{x},(D\appsep E_{x})}}}

\noindent
Initially the \linkbeta \rhs is a variable $D$ applied to the $E_x$.
The first unification problem results in $\sigma =
\{A \mapsto \lambda x.x\}$. In turn this instantiation
triggers progress \noteE{which rule?} in first \linketa that is 
removed and $E$ is assigned to $\lambda x.x$.
Under this substitution the \linkbeta becomes
\linkbetaM{x}{C_x}{(D \appsep x)}, and by \progBetaLL
it is replaced with the following two links:
\linkbetaM{x}{C_x}{F_x} and
\noteE{ma allora il link ora sparisce perhè è in llambda?}
\linketaM{}{E}{\lambda x.D_x}. The second unification
problem assignes $a$ to $B$, that in turn activates
the second \linketa ($a$ is assigned to $C$), and then all the remaining links
are solved. The final \Ho substitution is $\sigma = \{A = \lambda x.x, B = a,
C_x = a, D = \lambda \}$ and is decompiled into $\rho = \{X \mapsto \lambda x.x,
Y \mapsto a\}$.\noteE{assegnament per D incompleto}
\noteE{alla fine non si usa anche la regola beta-rigid-head?}

>>>>

% make test ONLY=7004 TEX=tex
\printAlll
  {{{X,\lambda x.x},
    {\lambda x.(Y\appsep (X\appsep x)),f}}}
  {{{A,\lambda x.x},
    {B,f}}}
  {{{Y,D,0},
    {X,A,0}}}
  {{{\eta,,A,\lambda x.E_{x}},
    {\eta,,B,\lambda x.C_{x}},
    {\beta,x,C_{x},(D\appsep E_{x})}}}

\noindent
Initially the \linkbeta \rhs is a variable $D$ applied to the $E_x$.
The first unification problem results in $\sigma =
\{A \mapsto \lambda x.x\}$. In turn this instantiation
triggers $\linkStore_1$ by \progressetaleft 
and $E$ is assigned to $\lambda x.x$.
Under this substitution the \linkbeta becomes
\linkbetaM{x}{C_x}{(D \appsep x)}, and by \progBetaLL
it is replaced with the following two links:
\linkbetaM{x}{C_x}{F_x} and
\noteE{ma allora il link ora sparisce perhè è in llambda?}
\linketaM{}{E}{\lambda x.D_x}. The second unification
problem assignes $f$ to $B$, that in turn activates
the second \linketa ($f$ is assigned to $C$), and then all the remaining links
are solved. The final \Ho substitution is $\sigma = \{A _{} \mapsto \lambda x.x, 
B _{} \mapsto f, C _{x} \mapsto (f\appsep x), 
D _{} \mapsto f, E _{x} \mapsto x, F _{x} \mapsto C_{x} \}$ and is decompiled into $\rho = \{X \mapsto \lambda x.x,
Y \mapsto f\}$.
\noteE{alla fine non si usa anche la regola beta-rigid-head?}
